Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
added reference to the figures int eraction

Typically users are interested in different \emph{properties} of an instance, for example, a user is interested in a product and its price, rating, manufacturer and so on.  An instance's properties are displayed beneath it; selecting a property creates a \emph{path selection}, which dereferences all of the instances in a group that contain the selected property and displays their corresponding values.  For example, when a user selects the \emph{manufacturer} property for a product, all products in the same group with a manufacturer property will be dereferenced, causing the manufactueres to be displayed alongside their corresponding products.  When such a path selection is applied, the properties displayed are updated to be the set of properties of the \emph{terminating value of the path}, so that this value can be dereferenced further.  For example, once selecting a manufacturer, a user may want to know the product's manufacturer's reputation and selects their ``reputation score'' property, causing the previous path selection to be extended.

@@

\item That supporting the selection of different paths by structure lets values be selected using separate different paths - making it possible to easily cope with properties with different names, and even at levels -- select the appropriate values even between instances that exhibit both  terminological and structurally heterogeneity.
\end{enumerate}

@@

In order to remain consistent with the drag-and-drop interactions used throughout the interface, we decided that simply dragging an instance onto another instance was a likely intuitive way for people to specify that two things should be combined.  Although general, this can be tedious for groups of items; to support more efficient combination, we extended this to allow entire groups to be dropped on other groups.  When this is done, DataPalette attempts to identify matching pairs among items in the dragged and target groups by comparing each pairs' labels.  Only exact matches (modulo white space/underscores) are considered matches and automatically combined.  The rest are added to the target group as distinct elements, and may be explicitly combined by hand.  We are considering more sophisticated / less fragile approaches to matching in the future, which would make the system assistive.

@@

@@

@@

As we refined our designs, we arrived at four simple mechanisms to support data mixing.  These were combined with a number of simple interaction mechanisms that were borrowed from other systems

The ultimatel design of datapal

Interaction features 
	multiple paths selection
	sameas interactions
	visualisation of partial results

Design process

>>>>

Typically users are interested in different \emph{properties} of an instance, for example, a user is interested in a product and its price, rating, manufacturer and so on.  An instance's properties are displayed beneath it; selecting a property creates a \emph{path selection}, which dereferences all of the instances in a group that contain the selected property and displays their corresponding values.  For example, when a user selects the \emph{manufacturer} property for a product, all products in the same group with a manufacturer property will be dereferenced, causing the manufactueres to be displayed alongside their corresponding products.  When such a path selection is applied, the properties displayed are updated to be the set of properties of the \emph{terminating value of the path}, so that this value can be dereferenced further.  For example, once selecting a manufacturer, a user may want to know the product's manufacturer's reputation and selects their ``reputation score'' property, causing the previous path selection to be extended. This process is illustrated in Figure \ref{fig:multipathing}.

@@

\item Supporting dereferencing along different paths \emph{by structure} allows instances with different property names, and even sub-structures to be quickly consolidated by separate dereferencing, thereby effectively coping with terminological and structural hetereogeneity.
\end{enumerate}

@@

In order to remain consistent with the drag-and-drop interactions used throughout the interface, we decided that simply dragging an instance onto another instance was a likely intuitive way for people to specify that two things should be combined.  An illustration of this interaction is provided in Figure \ref{fig:sameas}. Although general, this can be tedious for groups of items; to support more efficient combination, we extended this to allow entire groups to be dropped on other groups.  When this is done, DataPalette attempts to identify matching pairs among items in the dragged and target groups by comparing each pairs' labels.  Only exact matches (modulo white space/underscores) are considered matches and automatically combined.  The rest are added to the target group as distinct elements, and may be explicitly combined by hand.  We are considering more sophisticated / less fragile approaches to matching in the future, which would make the system assistive.

@@

\subsubsection{Enumerated-type value consolidation}

Related to the concept of co-reference, we extended the drag-and-drop sameas support to also be used to consolidate inconsistant enumerated values of properties, such as ``Casual dining'' vs ``Relaxed'' so that they can be uniformly compared. This allows the creation of meaningful, de-duplicated histograms and other visualisations.

\subsubsection{Model-based brushing}

Since it can get confusing having an instance represented in multiple groups,

@@

\subsubsection{Adaptive visualisation modes}

@@

%% Interaction features 
%% 	multiple paths selection
%% 	sameas interactions
%% 	visualisation of partial results

%% Design process
